% Template for Degree Programme in Computer Science and Engineering Diploma Thesis v1.3.2019
% Authors: Mika Korhonen (original author), Pekka Pietikäinen, Christian Wieser, Teemu Tokola, Juha Kylmänen, Tuomas Holmberg and Tuomas Varanka.
% If you make any improvements to this template, please contact teemu.tokola@oulu.fi
%
% CHANGELOG
% 2023-01-31: Track changes has been turned on - TTo
% 2023-06-15: Improvements to avoid missing filling in some details: TODO's added to template (TTo)
% 2023-06-15: Changes to foreword, clarifications to indicate template is also for Bachelor thesis  (TTo)
% 2023-06-15: Example of a CC-BY figure added with reference in the footnotes (TTo)


\documentclass[a4paper, 12pt, titlepage]{report}
\usepackage[english]{di}

% Give different options here to the students. First argument goes into the metadata and it's easiest to just have the text they want in there
\usepackage[type={CC}, modifier={by}, version={4.0}]{doclicense-csetemplate}

\copyrighttext
  {Copyright \textcopyright\ \number\year\ \getauthorslist. Except otherwise noted, the reuse of this document is authorized under a Creative Commons 4.0 International (CC-BY-4.0) license.}
  {%
    \textcopyright{}
    \number\year\ \getauthorslist.\par
    \doclicenseThis % CC logo, needs transparency removed
    Exception: The figures  are not included in the license.
  }
  
% Abstracts are placed in the metadata of the PDF file, 
% so they cannot contain empty lines or special characters.
% Mathematic symbols should be fine (mathxmp option for pdfx package),
\abstract{This document provides general guidance for a degree student
  of Computer Science and Engineering in preparing his/her master's
  thesis. This guide defines the role of a thesis in the
  M.Sc. Degree, presents the actions to be taken in different phases
  of the thesis procedure and introduces the way that master’s thesis
  is written. The document has been formatted based on these
  guidelines to serve as an example how the thesis should look like.}

\tiivistelma{Näissä ohjeissa opastetaan valmistumisvaiheessa olevaa
  opiskelijaa diplomityön tekemisessä. Ohjeissa selvitetään työn asema
  diplomi-insinööritutkinnossa, kerrotaan toimenpiteet, joihin työn
  tekijän on ryhdyttävä työn eri vaiheissa, sekä määritellään
  yksityiskohtaisesti diplomityön kirjallinen rakenne. Ohje on
  muotoiltu noudattaen näitä kirjoitusohjeita ja toimii siten
  esimerkkinä, miltä diplomityön tulisi näyttää.}

% Keywords are also included in the PDF metadata, and cannot contain any
% special characters. Separate them with \spc

\keywords{M.Sc. degree\spc master’s thesis instructions\spc structure of a master’s thesis}
\avainsanat{diplomi-insinöörin tutkinto\spc diplomityön ohjeet\spc diplomityön rakenne}

%%%%%%%%%%%%%%%%%%%%% SET YOUR INFORMATION HERE %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{TODO: Bachelor's and Diploma Thesis Guide}
\otsikko{TODO: Kandidaatintyön ja diplomityön teko-ohjeet}

\firstname{Author}
\lastname{One}

% Please choose the correct type of thesis and the language used
\thesis{Master} % {Bachelor | Master}

%Names of other authors can be added here
\firstnametwo{Author}
\lastnametwo{Two}
\firstnamethree{Author}
\lastnamethree{Three}
%Do not remove or comment the extra names if you do not need them, leave them empty instead


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\headertitlecap automatically creates headers with TitleCaps (Capitalizes the First Letter in Each Word) for H0, H2, and H3. Words not to be capitalized can be changed in di.sty
\headertitlecap

% Add your bibliographies here. You can use several
\addbibresource{citations.bib}

\begin{document}

\hypersetup{pageanchor=false}
\maketitlepage
    \pagenumbering{arabic}
    \setcounter{page}{1}
    \hypersetup{pageanchor=true}
    \makecopyrightpage{}
  
    \IfLang{\MainLang}{finnish}{
      \input{Chapters/tiivistelma}
      \input{Chapters/abstract}
      \selectlanguage{finnish}
    } {
      \input{Chapters/abstract}
      \input{Chapters/tiivistelma}
      \selectlanguage{english}
    }
    \contents %Insert table of contents
    \input{Chapters/foreword}
    \input{Chapters/abbreviations}
    
    %sets the dots for numbered chapters in table of contents
    \addtocontents{toc}{\protect\renewcommand{\protect\cftchapleader}{\protect\cftdotfill{\cftdotsep}}}

    \chapter{Introduction} %Set the name of a new chapter
        \label{introduction} %Create a label for referencing purposes (\charef{.})
        \pagenumbers
        \input{Chapters/introduction} %Input the contents of the chapter from a separate file
    
    \chapter{General outline for thesis projects}
        \label{relatedwork}
        \input{Chapters/relatedwork}
    
    \chapter{Thesis writing instructions}
        \label{implementation}
        \input{Chapters/implementation}
    
    \chapter{The literary structure of a thesis}
        \label{experiments}
        \input{Chapters/experiments}
    
    \chapter{Summary}
        \label{summary}
        \input{Chapters/summary}
    
    \printbibliography[heading=bibnumbered, title=\mybibname]

    \startappendix
    \chapter{Appendices}
        \input{Chapters/appendices}

\end{document}
